---
title: "Practical Machine Learning Course Assignment"
author: "Ruth Akintunde"
date: "Sunday, June 21, 2015"
output: html_document
---
### Executive Summary


### Data Processing

```{r}
library(caret)
pmltraining<-read.csv("pml-training.csv",na.strings=c("","NA","#DIV/0!"))

pmltraining<-pmltraining[,colSums(is.na(pmltraining))==0]
pmltraining<-pmltraining[,-c(1:7)]

set.seed(1445)
inTrain<-createDataPartition(y=pmltraining$classe,p=0.6,list=FALSE)
training<-pmltraining[inTrain,]
test<-pmltraining[-inTrain,]
```

## Now we have our train and test sets. Let's create a prediction model with trees

```{r}
modFitTrees<-train(classe~.,method="rpart",data=training)
pred<-predict(modFitTrees$finalModel,training, type = "class")
confusionMatrix(pred,training$classe)


```
* We can see from our results in R, the accuracy is very low, so we do further analysis with random forest model, which is known to produce models with high accuracy


```{r}
modFitRandomForest<-train(classe~.,method="rf",data=training,trControl=trainControl(method="cv",number = 5),prox=TRUE)
pred2<-predict(modFitRandomForest$finalModel,training, type="class")
confusionMatrix(pred2,training$classe)

```

Let us employ our model to the test data
```{r}


predTest<-predict(modFitRandomForest$finalModel,test, type="class")
confusionMatrix(predTest,test$classe)


```



### Project Submission



Our model is "modFitRandomForest" as seen above with high accuracy
```{r}

newtest<-read.csv("pml-testing.csv",na.strings=c("","NA","#DIV/0!"))
newtest<-newtest[,colSums(is.na(newtest))==0]
newtest<-newtest[,-c(1:7)]

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
predTest2<-predict(modFitRandomForest$finalModel,newtest, type="class")
pml_write_files(predTest2)

```
